Racial and Ethnic Differences in ETI: Outcomes

### 2024-10-24 Kamyron Jordan/Racial and Ethnic Differences in ETI/racial_and_ethnic_differences_in_eti_outcomes.qmd
Update racial_and_ethnic_differences_in_eti_outcomes.qmd

```{r}
# Fit mixed model with change point
change_mod <- lmer(
  gli_fev1_ppred_rn ~ Years * Race +
    slope_change_years * Race + age_group + Insurance + (1 | eDWID),
  data = encounter
)
# Model plot
mod_df <- change_mod@frame
mod_df$ind_pred <- predict(change_mod)
mod_df$pop_pred <- predict(change_mod, re.form = NA)
ggplot(mod_df, aes(x = Years)) +
  geom_point(aes(y = gli_fev1_ppred_rn, group = eDWID),
    alpha = 0.01, show.legend = F, shape = "."
  ) +
  geom_line(aes(y = ind_pred, group = eDWID),
    alpha = 0.01, show.legend = F
  ) +
  geom_line(aes(y = pop_pred, group = Race, colour = Race)) +
  xlab("Years from ETI Start") +
  theme_classic()
# Model summary
change_mod %>% gtsummary::tbl_regression()
```

>>>>

```{r}
# Fit mixed model with change point
change_mod <- lmer(
  gli_fev1_ppred_rn ~ Years * Race +
    slope_change_years * Race + age_group + Insurance + (1 | eDWID),
  data = encounter
)
# EMMs
emm = emmeans(change_mod,spec = ~Years+Race)

# Model plot
mod_df <- change_mod@frame
mod_df$ind_pred <- predict(change_mod)
pop_dat = mod_df %>% select(Years:Insurance)
pop_dat$pred <- predict(change_mod, re.form = NA,newdata = pop_dat)
pop_dat = pop_dat%>% distinct()
ggplot(mod_df, aes(x = Years)) +
  geom_point(aes(y = gli_fev1_ppred_rn, group = eDWID),
    alpha = 0.01, show.legend = F, shape = "."
  ) +
  geom_line(aes(y = ind_pred, group = eDWID),
    alpha = 0.01, show.legend = F
  ) +
  geom_line(data = pop_dat,aes(y = pred, group = Race, colour = Race)) +
  xlab("Years from ETI Start") +
  theme_classic()
# Model summary
change_mod %>% gtsummary::tbl_regression()
```
